---
title: 'Sentimental Analysis on Latest version of ios (ios 16.1.1) and android (android
  12) phones '
author: "| \\textit{Group No}: 11\n|\n| \\textit{Group Members}: \n"
date: '2022-11-28'
output:
  beamer_presentation: default
  powerpoint_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## AIM

Our aim is to analyze and visualize Twitter  data and the sentiment of obtained data, which could be used by both Apple and Google for both marketing and technical changes to their current or future products.

- The project is about comparing the latest versions of two contrasting operating systems, named __IOS16.1.1__ and __Android12__.
- OS is created by Apple and Android is maintained by Google.



## WORK FLOW

- twitter hash tags used: __#android12__ , __#ios 16.1.1__
- Total data count : 2000 twitters form each hash tag



## Description of Data - Frequency of Twitter statuses


```{r , basic_plot,eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE, results='hide', fig.dim = c(15, 6)}
require(rtweet)
require(ggplot2)
require(dplyr)
require(ggthemes)
require(readr)
require(jsonlite)
require(tidytext)
require(tidyr)
library(gridExtra) 
library(widyr)
library(ggplot2)
library(igraph)
library(ggraph)

rt<-stream_in(file("android12.json"))

ggp1<-ts_plot(rt, "5 mins") +
  theme_minimal() + # white background 
  theme(plot.title = element_text(face = "bold")) + # boldface title
  labs(
    x = NULL, y = NULL, # no labels on the axes
    title = " #Android12",
    subtitle = "Twitter status (tweet) counts aggregated using 5-minutes intervals",
    caption = "Source: Data collected from Twitter's REST API via rtweet"
  ) + 
  theme(axis.text.x = element_text(size = 10), 
          axis.text.y = element_text(size = 10), 
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          legend.text = element_text(size = 10),
          title = element_text(size = 14))  

rt2<-stream_in(file("ios16_1_1.json"))
ggp2<-ts_plot(rt2, "5 mins") +
  theme_minimal() + # white background 
  theme(plot.title = element_text(face = "bold")) + # boldface title
  labs(
    x = NULL, y = NULL, # no labels on the axes
    title = " #ios16_1_1 ",
    subtitle = "Twitter status (tweet) counts aggregated using 5-minutes intervals",
    caption = "Source: Data collected from Twitter's REST API via rtweet"
  ) + 
  theme(axis.text.x = element_text(size = 10), 
          axis.text.y = element_text(size = 10), 
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          legend.text = element_text(size = 10),
          title = element_text(size = 14))  
grid.arrange(ggp1, ggp2, ncol=2, nrow =1)          # Apply grid.arrange function
```

## Wordcloud for Tweets

```{r , eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE, results='hide'}
library(wordcloud)
library(wordcloud2)
library(maps)
library(httpuv)
library(reshape2)
library(tidyverse)


ios_tweets <- stream_in(file("ios16_1_1.json"))
android_tweets <-stream_in(file("android12.json"))

#stripped text - removing characters only,not punctuations

ios_tweets$stripped_text <- gsub("http.*","",  ios_tweets$text)
ios_tweets$stripped_text <- gsub("https.*","", ios_tweets$stripped_text)
ios_tweets$stripped_text <- gsub("amp","", ios_tweets$stripped_text)

android_tweets$stripped_text <- gsub("http.*","",  android_tweets$text)
android_tweets$stripped_text <- gsub("https.*","", android_tweets$stripped_text)
android_tweets$stripped_text <- gsub("amp","", android_tweets$stripped_text)
head(android_tweets$stripped_text)

# Let's remove punctuation, convert to lowercase, add id for each tweet:

ios_tweets_clean <- ios_tweets%>%
  select(stripped_text) %>% 
  mutate(tweetnumber = row_number()) %>% # create new variable denoting the tweet number
  unnest_tokens(word, stripped_text)

android_tweets_clean <- android_tweets %>%
  select(stripped_text) %>% 
  mutate(tweetnumber = row_number()) %>% # create new variable denoting the tweet number
  unnest_tokens(word, stripped_text)

ios_tweets_clean<- ios_tweets_clean %>% mutate(topic = "ios16.1.1")
android_tweets_clean<- android_tweets_clean %>% mutate(topic = "android12")

both_tweets_clean <- rbind(ios_tweets_clean,android_tweets_clean)


# load list of stop words - from the tidytext package
data("stop_words")
#
# the lexicon is the source of the stop word.
#

# remove stop words from your list of words

ios_cleaned_tweet_words_2 <- ios_tweets_clean %>%
  anti_join(stop_words) # return all rows from ios16.1.1_tweets_clean where there are not matching values in stop_words
#create our own stop words

android_cleaned_tweet_words_2 <- android_tweets_clean %>%
  anti_join(stop_words) # return all rows from android12_tweets_clean where there are not matching values in stop_words
#create our own stop words

my_stop_words <- data.frame(word = c("ios", "16.1.1", "iphone",'anroid','12','screen','apple','battery'))
#
#
# remove our own stopwords from the list of words too
android_cleaned_tweet_words_2<- android_cleaned_tweet_words_2 %>%
  anti_join(my_stop_words) 

# remove our own stopwords from the list of words too
ios_cleaned_tweet_words_2<- ios_cleaned_tweet_words_2 %>%
  anti_join(my_stop_words) 

ios_cleaned_tweet_words_2<- ios_cleaned_tweet_words_2 %>% mutate(topic = "ios16.1.1")
android_cleaned_tweet_words_2<- android_cleaned_tweet_words_2%>% mutate(topic = "android12")

both_tweets_clean1 <- rbind(ios_cleaned_tweet_words_2,android_cleaned_tweet_words_2)


# the count of each word / the total count

ios_cleaned_tweet_words_3 <- ios_cleaned_tweet_words_2 %>%
  count(word, sort = TRUE) %>% 
  mutate(freq = n / sum(n))

android_cleaned_tweet_words_3 <- android_cleaned_tweet_words_2 %>%
  count(word, sort = TRUE) %>% 
  mutate(freq = n / sum(n))

ios_cleaned_tweet_words_3<- ios_cleaned_tweet_words_3 %>% mutate(topic = "ios16.1.1")
android_cleaned_tweet_words_3<- android_cleaned_tweet_words_3%>% mutate(topic = "android12")

both_tweets_clean2 <- rbind(ios_cleaned_tweet_words_3,android_cleaned_tweet_words_3)

par(mfrow=c(1,2))

with(ios_cleaned_tweet_words_3,
     wordcloud(word,freq,
               min.freq = 1,
               max.words = 100,
               random.order = FALSE, rot.per = 0.50,
               colors = brewer.pal(8, "Dark2"), 
               scale = c(3, 0.1)))

title(main = "#ios16.1.1", 
      cex.main = 1) # Controls the size of the title


with(android_cleaned_tweet_words_3, 
     wordcloud(word, freq, 
               min.freq = 1, 
               max.words = 100,
               random.order = FALSE,rot.per = 0.35,
               colors = brewer.pal(8, "Dark2"), 
               scale = c(3, 0.1)))

title(main = "#android12", 
      cex.main = 1, sub="Sub-title") # Controls the size of the title


```
##Positive and negative wordcloud


```{r , eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE, results='hide'}

par(mfrow=c(1,2)) #divide the windows(for the graph) to two 

ios_cleaned_tweet_words_2%>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),  #creating positive and negative wordcloud
                   max.words = 100)%>%
  
  title(main = "Wordcloud with sentiment for Tweets containing ios16.1.1", 
        cex.main = 1)

android_cleaned_tweet_words_2%>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"), #creating positive and negative wordcloud
                   max.words = 100)

title(main = "Wordcloud with sentiment for Tweets containing android12", 
      cex.main = 1)
```
## Sentiment Scores Analysis

```{r , eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE, results='hide'}
ios_sentiment <- ios_cleaned_tweet_words_2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(tweetnumber, sentiment) %>%
  spread(sentiment, n, fill = 0) %>% # negative and positive sentiment in separate columns
  mutate(score = positive - negative) # score = net sentiment (positive - negative)
head(ios_sentiment)

android_sentiment <- android_cleaned_tweet_words_2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(tweetnumber, sentiment) %>%
  spread(sentiment, n, fill = 0) %>% # negative and positive sentiment in separate columns
  mutate(score = positive - negative) # score = net sentiment (positive - negative)
head(android_sentiment)

# Add a variable to indicate the topic

ios_sentiment<- ios_sentiment %>% mutate(topic = "ios16.1.1")
android_sentiment<-android_sentiment %>% mutate(topic = "android12")

both_sentiment <- rbind(ios_sentiment,android_sentiment)
#
# Let's work out the mean score 
# We'll include it as a line and as a numerical value to our plot
#
sentiment_means_both <- both_sentiment %>% group_by(topic) %>% 
  summarize(mean_score = mean(score)) 


both_sentiment %>% filter(topic=="android12") %>% summarize(ave=mean(score))
both_sentiment %>% filter(topic=="ios16.1.1") %>% summarize(ave=mean(score))
#
# Barplot
#
ggplot(both_sentiment, 
       aes(x = score, # Sentiment score on x-axis
           fill = topic)) + # Fill bars with a colour according to the topic
  geom_bar() + # geom_bar will do the tabulation for you :-)
  geom_vline(aes(xintercept = mean_score), 
             data = sentiment_means_both) +
  # Add a vertical line at the mean scores, calculated and stored in sentiment_mean_both above
  geom_text(aes(x = mean_score, 
                y = Inf, 
                label = signif(mean_score, 3)), 
            vjust = 2, 
            data = sentiment_means_both) + 
  # Add the mean as a number; vjust moves it down from the top of the plot
  scale_x_continuous(breaks = -15:15, 
                     minor_breaks = NULL) + # Show integers; set this to a suitably large range
  scale_fill_manual(values = c("ios16.1.1" = "green", 
                               "android12" = "blue")) + # Specify your own colours
  labs(x = "Sentiment Score" , 
       y = "Number of tweets", 
       fill = "topic",title = "Counts on each sentimental scores of ios16.1.1 and android12") +
  facet_grid(topic ~ .) + 
  caption = "Source: Data collected from Twitter's REST API via rtweet"+
  theme(axis.text.x = element_text(size = 10), 
          axis.text.y = element_text(size = 10), 
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          legend.text = element_text(size = 10),
          title = element_text(size = 14),legend.position = "bottom", title = element_text(size = 14))# Legend on the bottom
   
```

```{r , eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE, results='hide'}
#Counting the sentiments of positive,negative and neutral emotions for overall sentiment
positive <-  nrow(subset(ios_sentiment, score >0))
negative = nrow(subset(ios_sentiment, score <0))
neutral = nrow(subset(ios_sentiment, score ==0))

#binding all the sentiments into a table
tab_ios<-rbind(positive,negative,neutral)

#Counting the sentiments of positive,negative and neutral emotions for overall sentiment
positive <-  nrow(subset(android_sentiment, score >0))
negative = nrow(subset(android_sentiment, score <0))
neutral = nrow(subset(android_sentiment, score ==0))

#binding all the sentiments into a table
tab_android<-rbind(positive,negative,neutral)

words = c('camera','battery','update') #The most used feature words obtained from wordcloud
i<-0
#Implementing a loop to create a table for positive, negative and neutral emotions for the above words
while (i<4){
  i=i+1 #looping through next iteration
  ios_tweets_words<-dplyr::filter(ios_tweets, grepl(words[i], stripped_text)) #only filtering tweets with the specific words ios16.1.1
  android_tweets_words<-dplyr::filter(android_tweets, grepl(words[i], stripped_text)) #only filtering tweets with specific words for android12
  
  #Dividing the words in a sentence using unnest token
  ios_tweets_clean_words <- ios_tweets_words %>%
    select(stripped_text) %>% 
    mutate(tweetnumber = row_number()) %>% # create new variable denoting the tweet number
    unnest_tokens(word, stripped_text)
  head(ios_tweets_clean_words)

  android_tweets_clean_words <- android_tweets_words %>%
    select(stripped_text) %>% 
    mutate(tweetnumber = row_number()) %>% # create new variable denoting the tweet number
    unnest_tokens(word, stripped_text)
  head(android_tweets_clean_words)
  
  #remove stop words
  ios_clean_words <- ios_tweets_clean_words %>%
    anti_join(stop_words) # return all rows from ios16.1.1_tweets_clean where there are not matching values in stop_words
  
  android_clean_words <- android_tweets_clean_words %>%
    anti_join(stop_words) # return all rows from android12_tweets_clean where there are not matching values in stop_words
  
  
  ### Calculate sentiment scores for each tweet
  # associate sentiment scores to each tweet
  ios_sentiment_words <- ios_tweets_clean_words %>%
    inner_join(get_sentiments("bing")) %>%
    count(tweetnumber, sentiment) %>%
    spread(sentiment, n, fill = 0) %>% # negative and positive sentiment in separate columns
    mutate(score = positive - negative) # score = net sentiment (positive - negative)
  head(ios_sentiment_words)
  
  android_sentiment_words <- android_tweets_clean_words %>%
    inner_join(get_sentiments("bing")) %>%
    count(tweetnumber, sentiment) %>%
    spread(sentiment, n, fill = 0) %>% #negative and positive sentiment in separate columns
    mutate(score = positive - negative) # score = net sentiment (positive - negative)
  head(android_sentiment_words)
  
#sentiments for positive, negative and neutral for (camera,battery,update)are added to a table
  tab_ios <-cbind(tab_ios,rbind(nrow(subset(ios_sentiment_words, score >0)),
        nrow(subset(ios_sentiment_words, score <0)),
        nrow(subset(ios_sentiment_words, score ==0))))

  tab_android<-cbind(tab_android,rbind(nrow(subset(android_sentiment_words, score >0)),
                      nrow(subset(android_sentiment_words, score <0)),
                      nrow(subset(android_sentiment_words, score ==0))))
  
}

#stacked graph
#ios16.1.1
par(mfrow=c(1,2)) #dividing the window to two
barplot(as.matrix(tab_ios[,1:4]),col = c("gold3","red","blue"),
        names.arg = c('overall','screen','battery','update'),
        args.legend = list(x = "top"),
        legend.text = c('positive','Negative','Neutral'),
        main = "sentiment for Tweets containing android12")#creating a bar plot for ios16.1.1

#android12
barplot(as.matrix(tab_android[,1:4]),col=c("gold3","red","blue"),
        names.arg = c('overall','screen','battery','update'),
        args.legend = list(x = "top"),
        legend.text = c('positive','Negative','Neutral'),
        main = "sentiment for Tweets containing android12")#creating a bar plot for android12


```

##  Analysis
```{r , eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE, results='hide'}
#load tweets for both operating systems
ios16 <- stream_in(file("ios16_1_1.json"))

android12 <- stream_in(file("android12.json"))

#clean text of tweets
android12$stripped_text <- gsub("http.*", "", android12$text)
android12$stripped_text <- gsub("https.*", "", android12$stripped_text)
android12$stripped_text <- gsub("amp", "", android12$stripped_text)

ios16$stripped_text <- gsub("http.*", "", ios16$text)
ios16$stripped_text <- gsub("https.*", "", ios16$stripped_text)
ios16$stripped_text <- gsub("amp", "", ios16$stripped_text)


#break down tweets into words
ios16_clean <- ios16 %>% select(stripped_text) %>% mutate(tweetnumber = row_number()) %>% unnest_tokens(word, stripped_text)

android12_clean <- android12 %>% select(stripped_text) %>% mutate(tweetnumber = row_number()) %>% unnest_tokens(word, stripped_text)

#add tweet numbers to original data
android12 <- android12 %>% mutate(tweetnumber = row_number())

ios16 <- ios16 %>% mutate(tweetnumber = row_number())

#load stop words
data("stop_words")

#measure sentiment of words in tweets
sentiment_android12_tweets <- android12_clean %>% inner_join(get_sentiments("bing")) %>% count(tweetnumber, sentiment) %>% spread(sentiment, n, fill = 0) %>% mutate(score = positive - negative)

sentiment_ios16_tweets <- ios16_clean %>% inner_join(get_sentiments("bing")) %>% count(tweetnumber, sentiment) %>% spread(sentiment, n, fill = 0) %>% mutate(score = positive - negative)

#add sentiment scores to original tweets
android12_sentiment_tweets <- android12

ios16_sentiment_tweets <- ios16

android12_sentiment_tweets$sentiment_score <- sentiment_android12_tweets$score[match(android12_sentiment_tweets$tweetnumber, sentiment_android12_tweets$tweetnumber)]

ios16_sentiment_tweets$sentiment_score <- sentiment_ios16_tweets$score[match(ios16_sentiment_tweets$tweetnumber, sentiment_ios16_tweets$tweetnumber)]

#add category factor to tweets
android12_sentiment_tweets <- android12_sentiment_tweets %>% mutate(category = factor(ifelse(grepl("price", android12_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "price", 
                                                     ifelse(grepl("cost", android12_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "price",
                                                            ifelse(grepl("safety", android12_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "safety",
                                                                   ifelse(grepl("safe", android12_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "safety",
                                                                          ifelse(grepl("service", android12_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "service",
                                                                                ifelse(grepl("support", android12_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "service", "other"))))))))

ios16_sentiment_tweets <- ios16_sentiment_tweets %>% mutate(category = factor(ifelse(grepl("price", ios16_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "price", 
                                                                                             ifelse(grepl("cost", ios16_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "price",
                                                                                                    ifelse(grepl("safety", ios16_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "safety",
                                                                                                           ifelse(grepl("safe", ios16_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "safety",
                                                                                                                  ifelse(grepl("service", ios16_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "service",
                                                                                                                         ifelse(grepl("support", ios16_sentiment_tweets$stripped_text, fixed = TRUE) != FALSE, "service", "other"))))))))

#create factors for topics and overall sentiment
topics <- factor(c("price", "safety", "service", "other"))

sentiment_categories = factor(c("positive", "negative", "neutral"))

#add overall sentiment factor to tweets
android12_sentiment_tweets <- android12_sentiment_tweets %>% mutate(sentiment = factor(ifelse(sentiment_score < 0, "negative", ifelse(sentiment_score > 0, "positive", "neutral"))))

ios16_sentiment_tweets <- ios16_sentiment_tweets %>% mutate(sentiment = factor(ifelse(sentiment_score < 0, "negative", ifelse(sentiment_score > 0, "positive", "neutral"))))

par(mfrow=c(1,2))#divide the graph window into two
#Android plot
android12_sentiment_tweets %>%
  drop_na(sentiment) %>%
  subset(category != "other") %>%
ggplot(aes(x = category, y = sum(category == topics), fill = sentiment)) +
  geom_bar(stat = "identity", position = "stack", ) +
  theme_minimal() +
  
  labs(x = "Tweet Topic Category", y = "Number of tweets", title = "Stacked Bar Chart showing the number of tweets and sentiment in 3 categories (Android 12)", caption = "Source: Twitter's REST API via RTweet")

#ios plot
ios16_sentiment_tweets %>%
  drop_na(sentiment) %>%
  subset(category != "other") %>%
  ggplot(aes(x = category, y = sum(category == topics), fill = sentiment)) +
  geom_bar(stat = "identity", position = "stack", ) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10), 
          axis.text.y = element_text(size = 10), 
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          legend.text = element_text(size = 10)) +
  labs(x = "Tweet Topic Category", y = "Number of tweets", title = "Stacked Bar Chart showing the number of tweets and sentiment in 3 categories (IOS 16.1.1)", caption = "Source: Twitter's REST API via RTweet")
```

##Bigram
```{r , eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE, results='hide'}

ios_bigram<- ios_cleaned_tweet_words_2 %>%
  pairwise_count(word,tweetnumber, sort = TRUE, upper = FALSE) #
  
  par(mfrow=c(1,2))

  set.seed(1234)
ios_bigram %>%
  dplyr::filter(n >= 20) %>%#filtering the pair counts used more than 20
  graph_from_data_frame() %>%
  ggraph(layout = 'kk') +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "cyan4") + #formatting nodes
  geom_node_point(size = 5) +
geom_node_text(aes(label = name), repel = TRUE,
               point.padding = unit(0.2, "lines")) + #setting the sizes of nodes
  labs(subtitle = 'Bigram for ios16.1.1',plot.subtitle=element_text(size = 14))+
  theme_void()

 android_bigram %>%
    dplyr::filter(n >= 200) %>%
    graph_from_data_frame() %>%
    ggraph(layout = 'kk') +
    geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "cyan4") +
    geom_node_point(size = 5) +
    geom_node_text(aes(label = name), repel = TRUE,
                   point.padding = unit(0.2, "lines")) + #setting the sizes of nodes
    labs(subtitle = 'Bigram for android12',plot.subtitle =element_text(size = 14))
  theme_void()

```
## T test

```{r , eval = TRUE, echo = FALSE, warning = FALSE, message = TRUE, results='hold',fig.dim = c(15, 6)}
#T-Test for sentimental score of ios16.1.1 and android12
ggplot(both_sentiment, aes(x = topic , y = score, fill = topic)) + 
  geom_boxplot(varwidth = TRUE) +
  labs(x = "Android12 vs ios16.1.1", y = "Sentiment of each tweet",caption = "Source: Twitter's REST API via RTweet") 
  theme(axis.text.x = element_text(size = 10), 
          axis.text.y = element_text(size = 10), 
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          legend.text = element_text(size = 10))

t.test(score ~ topic, data = both_sentiment , var.equal = TRUE)
#


```

## Discussion 
- The overall sentiments are changing over time to time
-This twitter data set has shown a __reasonable difference__ in the positive sentiment of android12 and ios16.1.1

- From the observation from wordclouds the following words can be given importance in future researches.
ios16.1.1 - jailbreak,cydia
android12 - camera, kids offer
-The following words should be taken into consideration by the employers
| Brand   |  Positive    |  Negative  |
|:-------:|:------------:|:-----------|
|ios16.1.1|accurate      |stuck       |
|android12|fast         |scratches    |

- when considering the screen, update, and battery android12 has received positive feedback and conversely ios16.1.1 received negative feedback.

- Future research must use twitter data covering a long period inorder to obtain a decision for the two brands.


## Conclusion
- The overall __positive__ emotion of the __android12__ has __exceeded__ the __ios16.1.1__
- The __short term__ twitter data __cannot__ be used to give a final decision on which brand has got the positive emotion as the __emotions can change over time to time__

## References 




